\documentclass[11pt]{article}
\textwidth 7.5in
\textheight 10in
\oddsidemargin -.5in
\evensidemargin -.5in
\topmargin -1in    
\usepackage{graphics}        
\usepackage{graphicx}
\usepackage{amsmath,amsthm,amscd,amssymb}
\usepackage{latexsym}
\usepackage{upref}
\begin{document}
\newcommand{\dsp}{\displaystyle}
\newcommand{\ihat}{{\bf{i}}}
\newcommand{\jhat}{{\bf{j}}}
\newcommand{\khat}{{\bf{k}}}
\newcommand{\Fhat}{{\bf{F}}}
%\pagestyle{headings}
%\markright{MATH 1120 Lab Worksheet \#1}

\thispagestyle{empty}

\noindent
\sffamily
\begin{center}
\rule{7.5in}{2pt}

\vspace{.2in}

\begin{tabular}{p{4in}p{3.5in}}
MATH 3025

\vspace{.2in}

Mathematica Lab \#2
& 
NAME:  $_{\rule{2.5in}{1pt}}$

\vspace{.2in}

Due Monday March 6th 2023 by 11:59 P.M.
\\*[.2in]
\end{tabular}
\rule{7.5in}{2pt}

\vspace{.1in}
All work is to be done in a programming notebook. \\
 Please refer to the blackboard site for commands and examples. \\
 Submissions must be made electronically to Blackboard. \\
   You will be graded on the output that I am able to generate from your commands.
\end{center}
\begin{tabular}{*{26}{|c}|}\hline
A&B&C&D&E&F&G&H&I&J&K&L&M&N&O&P&Q&R&S&T&U&V&W&X&Y&Z\\ \hline
1&2&3&4&5&6&7&8&9&10&11&12&13&14&15&16&17&18&19&20&21&22&23&24&25&26\\ \hline
\end{tabular}

\begin{enumerate}
%\item Let $a$ be the letter that corresponds to your first initial.  Consider the functions
%\[f(x)=\arcsin\left(\frac xa\right)\quad\quad\quad g(x)=a-x^2\]
%\begin{enumerate}
%\item Graph both functions on the same coordinate axis.
%\item Find the points of intersection of the functions.
%\item Find the area of the region bounded by the curves.
%\end{enumerate}
\item Consider the function
\[
h(x)=\frac{4x^3-27x^2+5x-32}{30x^5-13x^4+50x^3-286x^2-299x-70}
\]
\begin{enumerate}
\item Find the partial fraction decomposition.  The `apart' command works nicely for this.
\item Integrate using the decomposition that you found.
\item Integrate using the original function.
\item Explain in complete sentences any discrepancies between the two.
\end{enumerate}
\item Using the function $g(x)=\dfrac{\cos^2x}{x^2}$.
\begin{enumerate}
\item Compute $\dsp \int_1^t g(x)\ dx$ for $t=2,5,10,100,1000, \text{and } 10000$.
\item In complete sentences, explain what would happen if $t\to\infty$. 
\item Let $f(x)=\dfrac1{x^2}$. Graph both $g(x)$ and $f(x)$ on the same axis.  Use your graph to explain why $\dsp \int_1^\infty g(x)\ dx $ is convergent. (Comparison Test)
\end{enumerate}
\item Consider the curve $y=\log_a x$, where $a$ is the first initial of you first name.  (if $a=1$, please use $a=e$, Euler's number)
\begin{enumerate}
\item Graph the curve from the points $(1,0)$ to $(2,\log_a2)$.
\item Calculate the length of the arc between those points.  (It may be necessary to use nintegrate) %no nitegrate in sympy...
\end{enumerate}
\end{enumerate}
\end{document}





