\documentclass[11pt]{article}
\textwidth 7.5in
\textheight 10in
\oddsidemargin -.5in
\evensidemargin -.5in
\topmargin -1in    
\usepackage{graphics}        
\usepackage{graphicx}
\usepackage{amsmath,amsthm,amscd,amssymb}
\usepackage{latexsym}
\usepackage{upref}
\usepackage{hyperref}
\begin{document}
\newcommand{\dsp}{\displaystyle}
\newcommand{\ihat}{{\bf{i}}}
\newcommand{\jhat}{{\bf{j}}}
\newcommand{\khat}{{\bf{k}}}
\newcommand{\Fhat}{{\bf{F}}}
%\pagestyle{headings}
%\markright{MATH 1120 Lab Worksheet \#1}

\thispagestyle{empty}

\noindent
\sffamily
\begin{center}
\rule{7.5in}{2pt}

\vspace{.2in}

\begin{tabular}{p{4in}p{3.5in}}
MATH 3025

\vspace{.2in}

Computer Lab \#0
& 
NAME:  $_{\rule{2.5in}{1pt}}$

\vspace{.2in}

Due Tuesday September 2nd 2025 by eod.
\\*[.2in]
\end{tabular}
\rule{7.5in}{2pt}

\vspace{.1in}
All work is to be done in a notebook with both code and written comments.  Please utilize the notebook structure to type comments in their own text boxes. \\
 Please refer to the blackboard and GitHub for commands and examples. 
%\bf Please delete all output before submitting.
\end{center}
%\begin{tabular}{*{26}{|c}|}\hline
%A&B&C&D&E&F&G&H&I&J&K&L&M&N&O&P&Q&R&S&T&U&V&W&X&Y&Z\\ \hline
%1&2&3&4&5&6&7&8&9&10&11&12&13&14&15&16&17&18&19&20&21&22&23&24&25&26\\ \hline
%\end{tabular}

\begin{enumerate}
\item Create a GitHub repository esspecially for this class.  Give the repo a descriptive name.  Initialize your repo with a readme.md file.  Put something in the readme file about the class.
\item Start a new Jupyter Notebook on \url{https://colab.research.google.com/}  You may need to create a google account (or sign into yours) to do so.  Add your name, the class and the assignment using headers and make it look pretty.
\item Save your notebook to GitHub using the drop down menu.  You will need to authorize this through your github account.  Save in your repo for this class.
\item Utilize markdown to give me your favorite function.  Tell me a little about why it is your favorite.
\item Define your function using python.  Compute a few interesting values.
\item Use sympy and define your favorite function again.  Compute the derivative and integral.
\item Save your file to GitHub.
\item Submit only the link to your github repo in the assignment blank on blackboard. 
\end{enumerate}
\end{document}





